---
title: "Evaluating Semi-Parametric Nowcasts of COVID-19 Hospital Admissions in Germany"
subtitle: "Summary"
author: Sam Abbott, Sebastian Funk
bibliography: ../../writeup/library.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/apa-numeric-superscript-brackets.csl
date: "`r format(Sys.Date(), format = '%B %d, %Y')`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    toc_depth: 4
    includes:
      before_body: ../header.html
      after_body: ../footer.html
---

```{r setup, echo = FALSE, cache = FALSE, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 330, warning = FALSE)
```

*This project is under active development. Current results are preliminary and may change as more data is collected or as the methodology is improved.**

# Background

COVID-19 hospitalisations in Germany are released by date of positive test rather than by date of admission as done in many other countries. This has some advantages when they are used as a tool for surveillance as these data have less time lag than if they by date of admission and are closer to the date of infection and so easier to link to underlying transmission dynamics and public health interventions. Unfortunately, however, when released in this way the latest data are right-censored meaning that final hospitalisations for a given day are initially underreported. This can lead to delayed or biased decision making. Fortunately, when data from a series of days is available we can estimate the level of censoring and provide estimates for the truncated hospitalisations adjusted for truncation with appropriate uncertainty. This is usually defined as a nowcast.

In this work, we aim to evaluate a series of novel semi-parametric nowcasting model formulations in real-time and provide an example workflow to allow others to do similarly using German COVID-19 hospitalisations by date of positive test at the national level both overall and by age group, and at the state level. This project is part of a [wider collaboration](https://covid19nowcasthub.de) assessing a range of nowcasting methods whilst providing an ensemble nowcast of COVID-19 Hospital admissions in Germany by date of positive test. This ensemble should be used for any policy-related work rather than the nowcasts provided in this repository. See [here](https://covid19nowcasthub.de) for more on this nowcasting collaboration.

# Methods

We follow the approach of Höhle and Heiden[@hohle] and consider the distribution of notifications by date of positive test and reporting delay conditional on the final observed count for each target dataset. This results in an estimation process where expected hospitalisations by date of positive test are estimated jointly with the delay distribution for each date of positive tes. When combined together, oonce an observation error model has been assumed (in our case a negative binomial model), estimated hospitalisations by date of report can be recovered. Aggregating these estimates then gives estimated hospitalisations by date of positive test adjusted for right censoring.

We evaluate consider two primary models and submit nowcasts from these models to the nowcasting hub. These are firstly a model that fits jointly to all age groups  


All models are implemented using the `epinowcast` R package [@epinowcast]. The nowcasting and evaluation pipeline is implemented using the `targets` R package[@targets]. All input data, interim data, and output data are available and should also be fully reproducible from the provided code. Please see the resources section for details.

# Resources

```{r, child = "../chunks/documentation.Rmd"}
```

# References
