---
title: "Evaluating Semi-Parametric Nowcasts of COVID-19 Hospital Admissions in Germany"
output: 
  rmarkdown::html_vignette: default
  pdf_document: default
  html_document:
    keep_md: true
    toc: true
    theme: united
  word_document: default
bibliography: library.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/apa-numeric-superscript-brackets.csl
header-includes:
   - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, eval = TRUE,
  fig.width = 9, fig.height = 9,
  dpi = 320,
  fig.path = "figures/"
)
```

```{r, message = FALSE}
library(forecast.vocs)
```

## Authors

S. Abbott (1)

Correspondence to: sam.abbott@lshtm.ac.uk

## Affiliations

1. Center for the Mathematical Modelling of Infectious Diseases, London School of Hygiene & Tropical Medicine, London WC1E 7HT, United Kingdom
## Abstract

**Background:**

**Methods:** 


**Results:** 


**Conclusions:** 

## Introduction

### Why

### What else has been done

### What did we do


## Methods

### Data

### Models

#### Fitting

Each forecast target was fit independently for each model using Markov-chain Monte Carlo (MCMC) in stan [@rstan]. 4 chains were used with a warmup of 1000 samples and a total of 4000 samples post warmup. Convergence was assessed using the R hat diagnostic [@rstan]. All forecasts used an adapt delta of 0.99 and a max treedepth of 15. See the Supplementary Information for further details.

### Evaluation

### Reproducibility

All analysis was carried out using R version 4.0.5 [@R]. The analysis pipeline described here is available as a `targets` workflow [@targets] along with an archive of all interim results. A dockerfile has been made available with the code to enhance reproducibility [@Boettiger:2015dw].

## Results

## Discussion

**Summary**

**Strengths and weaknesses**

- **Strengths:**

- **Weaknesses:**

**Literature comparison**

**Further work**

**Conclusions**

**Data availability**

Zenodo:

This project contains the following underlying data:


License: MIT

**Software availability**

Source code is available from: 

Archived source code at time of publication: 

License: MIT

**Grant information**

This work was supported by the Wellcome Trust through a Wellcome Senior Research Fellowship to SF [210758].

**Competing interests**

There are no competing interests. 

## References

<div id = 'refs'></div>
