---
title: "Supplementary information: Evaluating Semi-Mechanistic Nowcasts of COVID-19 Hospital Admissions in Germany"
output: 
  html_document:
    keep_md: false
    toc: true
    toc_float: true
    code_folding: hide
    theme: united
bibliography: library.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/apa-numeric-superscript-brackets.csl
header-includes:
   - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, eval = TRUE,
  fig.width = 9, fig.height = 9,
  dpi = 320,
  fig.path = "figures/"
)
```

## Authors

S. Abbott (1)

Correspondence to: sam.abbott@lshtm.ac.uk

## Affiliations

1. Center for the Mathematical Modelling of Infectious Diseases, London School of Hygiene & Tropical Medicine, London WC1E 7HT, United Kingdom
## Overview

This analysis uses the `targets` package for reproducibility. The full analysis structure can be seen below:

```{r, message = FALSE}
library(targets)
tar_glimpse()
```

## Data

## Models

## Model evaluation


## Real-world evaluation

## References

<div id = 'refs'></div>
